Manuscript Figures for Genome Biology

### 2018-09-17 manuscript_figures/manuscript_figures.Rmd
Edit subtitles Fig1 & Alignment of Fig S1 and S3

# Figure 2A: Not all methods control FDR at nominal alpha level
p1 <- plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +  
      ggtitle("Mean FDR (100 replications)") +
      scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02))

# Figure 2B: TPR of methods across nominal alpha level
p2 <- plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none")  +  
      ggtitle("Mean TPR (100 replications)") +
      scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02))

# Figure 2C: Total number of discoveries varied across method
p3 <- plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +
      ylab("Number of Rejections") +
      ggtitle("Mean Rejections (100 replications)") +
      scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02))

@@

# Figure 2E - upsetr plot - save separately
pdf(file.path(outdir, "Figure2E.pdf"), width = 8, height = 4, onefile=FALSE)
aggupset(de5, alpha=alpha, supplementary = FALSE, 
                       return_list = FALSE, nintersects = 12)
grid.text("Mean overlap Over 100 Replications", x = 0.65, y = 0.97, 
          gp = gpar(fontsize = 14, fontface = "bold"))
grid.text("E", x = 0.01, y = 0.97, 
          gp = gpar(fontsize = 22, fontface = "bold")) 
dev.off()

@@

FigA <- plot_grid(FigStrong + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigStrongT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2)

FigB <- plot_grid(FigWeak + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigWeakT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2)

@@

FigA <- plot_grid(FigStrong + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigStrongT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2, axis = "rlbt")

FigB <- plot_grid(FigWeak + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigWeakT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2, axis = "rlbt")

>>>>

# Figure 2A: Not all methods control FDR at nominal alpha level
p1 <- plotsim_average(res5d, met="FDR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +  
      ggtitle("FDR by alpha level") +
      scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02))

# Figure 2B: TPR of methods across nominal alpha level
p2 <- plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none")  +  
      ggtitle("TPR by alpha level") +
      scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02))

# Figure 2C: Total number of discoveries varied across method
p3 <- plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) +
      theme(legend.position="none") +
      ylab("Number of Rejections") +
      ggtitle("Rejections by alpha level") +
      scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02))

@@

# Figure 2E - upsetr plot - save separately
pdf(file.path(outdir, "Figure2E.pdf"), width = 8, height = 4, onefile=FALSE)
aggupset(de5, alpha=alpha, supplementary = FALSE, 
                       return_list = FALSE, nintersects = 12)
grid.text("Mean overlap of rejection sets", x = 0.65, y = 0.97, 
          gp = gpar(fontsize = 14, fontface = "bold"))
grid.text("E", x = 0.01, y = 0.97, 
          gp = gpar(fontsize = 22, fontface = "bold")) 
dev.off()

@@

FigA <- plot_grid(FigStrong + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigStrongT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2, align = "hv")

FigB <- plot_grid(FigWeak + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigWeakT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2, align = "hv")

@@

FigA <- plot_grid(FigStrong + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigStrongT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2, align = "hv")

FigB <- plot_grid(FigWeak + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)), 
                  FigWeakT + theme(legend.position="none") +  
                   scale_x_continuous("alpha cutoff", breaks=seq(0, 1, by=0.02)),
                 nrow = 2, align = "hv")
